MSB104_assignment1

### 2023-10-09 MSB104_assignment1.qmd
Update 09.10.23

```{r}
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_DE_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_DE_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we exclude the geom_smooth and instead use geom_line since this gives a accurate description of our data from Germany.
#| cap-location: bottom
#| fig-cap: "GDP per year."
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz1
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  #geom_smooth(se = FALSE, snap = 0.9)
  geom_line()
```

```{r}
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz2
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  #geom_smooth(se = FALSE, snap = 0.9)
  geom_line()
```

>>>>

```{r}
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_DE_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_DE_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we exclude the geom_smooth and instead use geom_line since this gives a accurate description of our data from Germany.
#| cap-location: bottom
#| fig-cap: "GDP per year."
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz1NORTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  #geom_smooth(se = FALSE, snap = 0.9)
  geom_line()
```

```{r}
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz2SOUTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  #geom_smooth(se = FALSE, snap = 0.9)
  geom_line()
```
